Computing exact restricted isometry constants via\\ mixed integer semidefinite programming

### 2015-01-08 RIP-MISDP-Paper/Paper_v1.tex
changed the alpha to Big M for left hand side in Asp08

\comment{Der ganze Absatz ist \"uberarbeitet, z.B.\ die RIR korrigiert
  (statt $(1 - \delta_k)/(1 + \delta_k)$). Korrekt?}
%
Definition~\ref{asymRIPdef} is a generalization of Definition~\ref{ripdef}
in the following sense: if the matrix~$A$ satisfies the RIP of order $k$
with RIC $\delta_k$, then it has a RIR of at most $(1 + \delta_k) / (1 -
\delta_k)$. Conversely, if $A$ has lower/upper RICs $\alpha_k$ and
$\beta_k$, respectively, then it will also satisfy~\eqref{rip} for
$\delta_k = \max \{1 - \alpha_k^2,\; \beta_k^2 - 1\}$. So $A$ has a small
RIC if and only if it has a large lower and a small upper RIC. But since
in~\eqref{rip} usually only one of the two inequalities will be sharp, the
asymmetric version yields more information about~$A$.

@@

\begin{equation*}
 \alpha_k^2 \geq \sup_{\rho \geq 0} \psi(\rho) - \rho k,
\end{equation*}
with 
\begin{equation*}
 \psi(\rho) = \min_{\Norm{x}{2} \leq 1} x\T \Sigma x + \rho \Norm{x}{0}.
\end{equation*}
In this case problem (\ref{Asp08}) has to be solved for $\Sigma = \alpha I - A\T A$, where $\alpha$ has to be big enough to make $\Sigma$ positive semidefinite again. If $\bar{\Psi}$ is the corresponding optimal solution, this implies
a lower bound on $\alpha_k$ as

>>>>

\comment{Der ganze Absatz ist \"uberarbeitet, z.B.\ die RIR korrigiert
  (statt $(1 - \delta_k)/(1 + \delta_k)$). Korrekt? Korrekt}
%
Definition~\ref{asymRIPdef} is a generalization of Definition~\ref{ripdef}
in the following sense: if the matrix~$A$ satisfies the RIP of order $k$
with RIC $\delta_k$, then it has a RIR of at most $(1 + \delta_k) / (1 -
\delta_k)$. Conversely, if $A$ has lower/upper RICs $\alpha_k$ and
$\beta_k$, respectively, then it will also satisfy~\eqref{rip} for
$\delta_k = \max \{1 - \alpha_k^2,\; \beta_k^2 - 1\}$. So $A$ has a small
RIC if and only if it has a large lower and a small upper RIC. But since
in~\eqref{rip} usually only one of the two inequalities will be sharp, the
asymmetric version yields more information about~$A$.

@@

\begin{equation*}
 \alpha_k^2 \geq \sup_{\rho \geq 0} \psi(\rho) - \rho k,
\end{equation*}
with 
\begin{equation*}
 \psi(\rho) = \min_{\Norm{x}{2} \leq 1} x\T \Sigma x + \rho \Norm{x}{0}.
\end{equation*}
In this case problem (\ref{Asp08}) or equivalently (\ref{Asp08Dual}) has to be solved for $\Sigma = M I - A\T A$, where $M$ has to be big enough to make $\Sigma$ positive semidefinite again. If $\bar{\Psi}$ is the corresponding optimal solution, this implies
a lower bound on $\alpha_k$ as
